Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-20 paper-ieee-trans.tex

\begin{IEEEbiography} [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/Ronchieri}}]{Elisabetta Ronchieri}
is a Computer Science Engineer at INFN (Istituto Nazionale di Fisica Nucleare - National Institute of Nuclear Physics) CNAF. Her main area of interest include software engineering issues such as software quality and software prediction model. She is also interested in (big and open) data analysis by using predictive techniques coming from various theories. such as Machine Learning.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography} [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/Ronchieri}}]{Elisabetta Ronchieri}
is a Computer Science Engineer at INFN (Istituto Nazionale di Fisica Nucleare - National Institute of Nuclear Physics) CNAF. She holds a PhD in Automation, Robotics and Bioengineering from the University of Pisa. Her main area of interest include software engineering issues, such as software quality and software prediction model. She is also interested in (big and open) data analysis by using techniques coming from various theories, such as Machine Learning.
\end{IEEEbiography}
